Extracting all spectra for NEON mapped stems

### 2020-09-02 R/spectral-lib.Rmd
updated the file paths
to keep all the spectral lib files in the analysis data directory

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#library(devtools)
#install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
library(sp)
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(Rtsne)
library(ggthemes)
```

@@

```{r get-veg-data}
# set output directory within the analysis/data/raw_data path 
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir)
dir.create(file.path(out_dir, 'data'))

@@

```{r read-map}
vegmap <- read_csv("data/filesToStack10098/stackedFiles/vst_mappingandtagging.csv") %>%
  filter(!is.na(stemAzimuth), !is.na(pointID))
vegind <- read_csv("data/filesToStack10098/stackedFiles/vst_apparentindividual.csv")
```

@@

```{r write-veg}
write_csv(veg, 'neon-veg.csv')
```

@@

species_counts %>%
  ggplot(aes(x = n, y = order)) +
  scale_x_log10() +
  geom_point(color = 'dodgerblue') +
  xlab('Number of mapped stem locations') +
  ylab('Order: commonest to rarest') +
  theme_minimal() +
  theme(panel.grid.minor = element_blank())
ggsave('~/Desktop/veg-freq.png', width = 4.5, height = 3)

@@

```{r extract-data}
spectra <- vector(mode = 'list', length = length(split_veg))
dir.create('hs_data', showWarnings = FALSE)
csv_dir <- file.path("hs_data", "tabular")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)

>>>>

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#library(devtools)
#install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
library(sp)
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(Rtsne)
library(ggthemes)
library(dplyr)
```

@@

```{r get-veg-data}
# VS-NOTE: set output directory within the analysis/data/raw_data path 
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir)
dir.create(file.path(out_dir, 'data'))

@@

```{r read-map}
vegmap <- read_csv(file.path(out_dir, "data", "filesToStack10098", "stackedFiles", 
                            "vst_mappingandtagging.csv")) %>%
  filter(!is.na(stemAzimuth), !is.na(pointID))
vegind <- read_csv(file.path(out_dir, "data", "filesToStack10098", "stackedFiles",
                             "vst_apparentindividual.csv"))
```

@@

```{r write-veg}
write_csv(veg, file.path(out_dir, "neon-veg.csv"))
```

@@

species_counts %>%
  ggplot(aes(x = n, y = order)) +
  scale_x_log10() +
  geom_point(color = 'dodgerblue') +
  xlab('Number of mapped stem locations') +
  ylab('Order: commonest to rarest') +
  theme_minimal() +
  theme(panel.grid.minor = element_blank())
ggsave(file.path(out_dir, "veg-freq.png"), width = 4.5, height = 3)

@@

```{r extract-data}
spectra <- vector(mode = 'list', length = length(split_veg))
dir.create(file.path(out_dir, "hs_data"), showWarnings = FALSE)
csv_dir <- file.path(out_dir, "hs_data", "tabular")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
